---
title: "Lab 01 - Hello R"
author: "John Mieszczanski"
date: "09/06/2021"
output: 
  html_document: 
    highlight: espresso
    theme: readable
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The three variables are `dataset`, `x`, and `y`.
```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>% 
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset is seen below:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
As we can see, there is essentially no linear relationship between `x` and `y` in the `dino_data` dataset!

### Exercise 3

Next, let's plot the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>% 
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset is seen below:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

As we can see, there is essentially no linear relationship between `x` and `y` in the `star_data` dataset! However, there is a slighly larger (negative magnitude) correlation in the `dino_data` dataset compared to the `star_data` dataset.

### Exercise 4

Next, let's plot the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset is seen below:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

As we can see, there is essentially no linear relationship between `x` and `y` in the `circle_data` dataset! However, there is a slighly larger (negative magnitude) correlation in the `circle_data` dataset compared to the `dino_data` dataset.

### Exercise 5

Now let's plot all 13 datasets in a 3 column grid using faceting:

```{r all_datasets, fig.height=7, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Lastly, we will print the correlation coefficients for each of the datasets:

```{r all-cor}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```

As we can see, `v_lines` has the largest magnitude of (negative) correlation and `dots` has the smallest magnitude of (negative) correlation. However, these magnitudes are so small that effectively none of the datasets have any meaninful linear correlation between `x` and `y`.